S2. Additional figures and table

### 2022-02-01 Manuscript/Manuscript.Rmd
file style up

out <- unlist(lapply(c(
	'Manuscript_Introduction.Rmd',
	'Manuscript_Methods.Rmd',
	'Manuscript_Results.Rmd',
	'Manuscript_Discussion.Rmd'
), knitr::knit_child, quiet = TRUE))

cat(out, sep = '\n')

```

>>>>

out <- unlist(lapply(c(
  "Manuscript_Introduction.Rmd",
  "Manuscript_Methods.Rmd",
  "Manuscript_Results.Rmd",
  "Manuscript_Discussion.Rmd"
), knitr::knit_child, quiet = TRUE))

cat(out, sep = "\n")
```

### 2022-02-01 Manuscript/Manuscript_Results.Rmd
file style up

wd <- ifelse(basename(getwd()) == 'Manuscript', dirname(getwd()), getwd())

@@

options(knitr.kable.NA = '')

knitr::opts_chunk$set(
	echo = FALSE,
	error = FALSE,
	message = FALSE,
	warning = FALSE,
	dpi = 400,
	cache = TRUE,
	cache.rebuild = FALSE
)

```

```{r load framework, cache.rebuild=TRUE, include=FALSE}
source(file.path('R', 'Setup.R'), local = knitr::knit_global())

# The following are already the default, but better be explicit
options(baysren.probs = c(.05, .5, .95))
options(baysren.sessions_folder = 'Sessions')
```

@@

session1_files <- get_session_files('Session1')
session2_files <- get_session_files('Session2')

@@

annotation_results <- summarise_annotations_by_session(remove_raw_data = TRUE)

```

@@

first_query <- import_data('Session_journal.csv') %>% 
    filter(Session_ID == 'Session1') %>% 
    with(Query[1])

@@

all_records <- source_summary[names(source_summary) != 'Total'] %>%
	sapply('[[', 'Records') %>% sum()

@@

session_summary <- summarise_annotations('Session1', remove_raw_data = FALSE)

num_first_labeling <- session_summary[1,]$tot_reviewed_

num_first_positives <- session_summary[1,]$Positives
num_first_negatives <- session_summary[1,]$Negatives

@@

var_importance <- extract_var_imp('Session1') %>%
	format_var_imp(as_data_frame = FALSE) %>%
	paste(collapse = ', ')

```

@@

```{r session 2}
new_query <- import_data('Session_journal.csv') %>% 
    filter(Session_ID == 'Session2') %>% 
    with(Query[1])

@@

session_summary <- summarise_annotations('Session2', remove_raw_data = FALSE)

@@

# Creating these summaries is quite demanding, so it's better to cache them
# explicitly
perf_file <- file.path('Manuscript', 'Performance_summary.rds')

if (!file.exists(perf_file)) {
	Performance <- list(
		s1 = get_session_files('Session1')$Annotations %>% last() %>%
			import_data() %>% estimate_performance(),
		s2 = get_session_files('Session2')$Annotations %>% last() %>%
			import_data() %>% estimate_performance()
	)

	write_rds(Performance, perf_file)

} else {
	Performance <- read_rds(perf_file)
}

@@

Performance$s1$plot +
	guides(color = 'none', fill = 'none') +
	ggtitle('Session 1') +
	Performance$s2$plot +
	ggtitle('Session 2') +
	theme(
		axis.title.y = element_blank()
	) &
	theme(
		legend.position = 'bottom'
	) &
	plot_layout(guides = 'collect')
```

>>>>

wd <- ifelse(basename(getwd()) == "Manuscript", dirname(getwd()), getwd())

@@

options(knitr.kable.NA = "")

knitr::opts_chunk$set(
  echo = FALSE,
  error = FALSE,
  message = FALSE,
  warning = FALSE,
  dpi = 400,
  cache = TRUE,
  cache.rebuild = FALSE
)
```

```{r load framework, cache.rebuild=TRUE, include=FALSE}
source(file.path("R", "Setup.R"), local = knitr::knit_global())

# The following are already the default, but better be explicit
options(baysren.probs = c(.05, .5, .95))
options(baysren.sessions_folder = "Sessions")
```

@@

session1_files <- get_session_files("Session1")
session2_files <- get_session_files("Session2")

@@

annotation_results <- summarise_annotations_by_session(remove_raw_data = TRUE)
```

@@

first_query <- import_data("Session_journal.csv") %>%
  filter(Session_ID == "Session1") %>%
  with(Query[1])

@@

all_records <- source_summary[names(source_summary) != "Total"] %>%
  sapply("[[", "Records") %>%
  sum()

@@

session_summary <- summarise_annotations("Session1", remove_raw_data = FALSE)

num_first_labeling <- session_summary[1, ]$tot_reviewed_

num_first_positives <- session_summary[1, ]$Positives
num_first_negatives <- session_summary[1, ]$Negatives

@@

var_importance <- extract_var_imp("Session1") %>%
  format_var_imp(as_data_frame = FALSE) %>%
  paste(collapse = ", ")
```

@@

```{r session 2}
new_query <- import_data("Session_journal.csv") %>%
  filter(Session_ID == "Session2") %>%
  with(Query[1])

@@

session_summary <- summarise_annotations("Session2", remove_raw_data = FALSE)

@@

# Creating these summaries is quite demanding, so it's better to cache them
# explicitly
perf_file <- file.path("Manuscript", "Performance_summary.rds")

if (!file.exists(perf_file)) {
  Performance <- list(
    s1 = get_session_files("Session1")$Annotations %>% last() %>%
      import_data() %>% estimate_performance(),
    s2 = get_session_files("Session2")$Annotations %>% last() %>%
      import_data() %>% estimate_performance()
  )

  write_rds(Performance, perf_file)
} else {
  Performance <- read_rds(perf_file)
}

@@

Performance$s1$plot +
  guides(color = "none", fill = "none") +
  ggtitle("Session 1") +
  Performance$s2$plot +
  ggtitle("Session 2") +
  theme(
    axis.title.y = element_blank()
  ) &
  theme(
    legend.position = "bottom"
  ) &
  plot_layout(guides = "collect")
```

### 2022-02-01 Manuscript/S2.Additional_outputs.Rmd
file style up

options(knitr.kable.NA = '')

knitr::opts_chunk$set(
	echo = FALSE,
	error = FALSE,
	message = FALSE,
	warning = FALSE,
	dpi = 400,
	cache = TRUE,
	cache.rebuild = FALSE
)

```

```{r load framework, cache.rebuild=TRUE}
source(file.path('R', 'Setup.R'))

# The following are already the default, but better be explicit
options(baysren.probs = c(.05, .5, .95))
options(baysren.sessions_folder = 'Sessions')
```

@@

s1_plot <- plot_predictive_densities('Session1')

s2_plot <- plot_predictive_densities('Session2')

s1_plot +
    guides(color = 'none', fill = 'none') +
    ggtitle('Session 1') +
    s2_plot +
    ggtitle('Session 2') +
    theme(
        axis.title.y = element_blank()
        ) &
    theme(
        legend.position = 'bottom'
    ) &
    plot_layout(guides = 'collect')
```

@@

var_importance_s1 <- extract_var_imp('Session1', num_vars = n_terms, score_filter = 0) %>%
	format_var_imp(as_data_frame = TRUE)

var_importance_s2 <- extract_var_imp('Session1', num_vars = n_terms, score_filter = 0) %>%
	format_var_imp(as_data_frame = TRUE)
```

@@

grid_out_params <- grid_out$best_by_rule %>% 
	mutate(Score = str_remove(Score, ' .+')) %>% 
	rename(
		`Cluster (mean score)` = Cluster,
		`Num. iterations` = Iter,
		`Positive matches` = Pos_labels,
		`Reviewed records` = Tot_labeled,
		`Score (Sens. x Eff.)` = Score,
		`Num. ensemble models` = Mods,
		`Uncertainty interval` = Quant,
		`Resampling` = Resamp,
		`Num. initial training records` = Init,
		`Positives oversampling multiplier` = Mult
	)

print(grid_out$plot & labs(y = 'Sens. x. Eff.'))

```

>>>>

options(knitr.kable.NA = "")

knitr::opts_chunk$set(
  echo = FALSE,
  error = FALSE,
  message = FALSE,
  warning = FALSE,
  dpi = 400,
  cache = TRUE,
  cache.rebuild = FALSE
)
```

```{r load framework, cache.rebuild=TRUE}
source(file.path("R", "Setup.R"))

# The following are already the default, but better be explicit
options(baysren.probs = c(.05, .5, .95))
options(baysren.sessions_folder = "Sessions")
```

@@

s1_plot <- plot_predictive_densities("Session1")

s2_plot <- plot_predictive_densities("Session2")

s1_plot +
  guides(color = "none", fill = "none") +
  ggtitle("Session 1") +
  s2_plot +
  ggtitle("Session 2") +
  theme(
    axis.title.y = element_blank()
  ) &
  theme(
    legend.position = "bottom"
  ) &
  plot_layout(guides = "collect")
```

@@

var_importance_s1 <- extract_var_imp("Session1", num_vars = n_terms, score_filter = 0) %>%
  format_var_imp(as_data_frame = TRUE)

var_importance_s2 <- extract_var_imp("Session1", num_vars = n_terms, score_filter = 0) %>%
  format_var_imp(as_data_frame = TRUE)
```

@@

grid_out_params <- grid_out$best_by_rule %>%
  mutate(Score = str_remove(Score, " .+")) %>%
  rename(
    `Cluster (mean score)` = Cluster,
    `Num. iterations` = Iter,
    `Positive matches` = Pos_labels,
    `Reviewed records` = Tot_labeled,
    `Score (Sens. x Eff.)` = Score,
    `Num. ensemble models` = Mods,
    `Uncertainty interval` = Quant,
    `Resampling` = Resamp,
    `Num. initial training records` = Init,
    `Positives oversampling multiplier` = Mult
  )

print(grid_out$plot & labs(y = "Sens. x. Eff."))
```
